\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}
\usepackage{graphicx}    % Required for inserting images.
\usepackage{amsmath,amssymb,gensymb}  % Advanced math formatting.
\usepackage{float}  % Required to force figure position.
\usepackage{lipsum} % For dummy text.
\usepackage{hyperref}
 

\begin{document}

\title{Calibration of a Three-dimensional Muon Detector Based on Scintillator Binary Optical Encoding\\[0.5ex] \small Team Dawson Technicolor}

\author{Milo Belarbi}
\author{David Birnbaum}
\author{Tykhon Byshkin}
\author{Matvey Chirchikov}
\author{Danah Dézémé}
\author{Arij Mohamedi} 
\author{Evan Parasol}
\author{Leandro Perez Moran}
\author{Ari Polterovich}
\author{Tian Yi Xia}
\author{Chun On Yu}
\author{Aljoscha Ziegler}
\author{Manuel Toharia}
\altaffiliation{Teacher}
\author{Joel Trudeau}
\altaffiliation{Teacher}

\affiliation{Dawson College, Montreal, Quebec, Canada}
\date{April 10, 2025}

\maketitle



%\begin{multicols}{2}

\section{Introduction}
\input{sections/introduction}

\section{Design}
\input{sections/design}


\vspace{40mm}
\section{Results}
\input{sections/results}

%\clearpage

\section{Experimental Proposal}
\input{sections/experiment}

\section{Outlook}
\input{sections/conclusion}

%TC:ignore
\section{Community outreach}
\input{sections/community_outreach}

%\end{multicols}

% Section: Acknowledgements
%\clearpage
\section{Acknowledgments}
\input{acknowledgements}

\clearpage
\section{Appendices}
\input{appendices}

\begin{thebibliography}{99}
% \cite{Spectrum of CRM}
\bibitem{Spectrum of CRM}
Gardner, M., et al., "The Momentum Spectrum of Cosmic Ray Muons near Sea Level in the Momentum Range 0.4--10 GeV/c." IOPScience. Accessed March 2022,
\url{https://iopscience.iop.org/article/10.1088/0370-1328/80/3/314/pdf}.

% \cite{hyperphysics}
\bibitem{hyperphysics}
Hyperphysics, "Atmospheric Muons." Georgia State University. Accessed March 2022,
\url{http://hyperphysics.phy-astr.gsu.edu/hbase/Particles/muonatm.html}.

% \cite{atmospheric muon}
\bibitem{atmospheric muon}
CERN, "Cosmic Rays: Particles from Outer Space." Accessed March 2022,
\url{https://home.cern/science/physics/cosmic-rays-particles-outer-space}.

\bibitem{pdg}
K.~Nakamura \textit{et al.} [Particle Data Group], J. Phys. G \textbf{37}, 075021 (2010),
doi:10.1088/0954-3899/37/7A/075021,
\url{https://pdg.lbl.gov/2011/reviews/rpp2011-rev-cosmic-rays.pdf}.



\bibitem{agc}
Kuttner, P. The rope memory: a permanent storage device. {\em Proceedings Of The November 12-14, 1963, Fall Joint Computer Conference}. pp. 45-57 (1963), \url{https://doi.org/10.1145/1463822.1463829}


\bibitem{wls}Worstell, W., Doulas, S., Johnson, O. \& Lin, C. Scintillator crystal readout with wavelength-shifting optical fibers. {\em Proceedings Of 1994 IEEE Nuclear Science Symposium - NSS'94}. \textbf{4} pp. 1869-1873 vol.4 (1994)
\url{https://dl.acm.org/doi/pdf/10.1145/1463822.1463829}


\end{thebibliography}
%TC:endignore

\end{document}